---
title: "Agentic AI Demo Report"
format:
  html:
    toc: true
  pdf:
    toc: true
    pdf-engine: tectonic
  docx: default
  gfm: default
freeze: auto
execute:
  echo: true
---

```{r}
#| label: setup
#| message: false
library(yaml)
library(readr)

metrics_path <- here::here("outputs","results","metrics.yml")
cleaning_path <- here::here("outputs","results","cleaning.yml")
fig_path <- here::here("outputs","figures","rt_hist.png")
freq_tidy_path <- here::here("outputs","results","character_frequency_model_tidy.csv")
freq_glance_path <- here::here("outputs","results","character_frequency_model_glance.csv")
freq_fig_path <- here::here("outputs","figures","character_frequency_rt_vs_freq.png")

metrics <- yaml::read_yaml(metrics_path)
cleaning <- yaml::read_yaml(cleaning_path)
freq_model_tidy <- read_csv(freq_tidy_path, show_col_types = FALSE)
freq_model_glance <- read_csv(freq_glance_path, show_col_types = FALSE)
N <- as.integer(metrics$n_obs)

# helpers for formatting
fmt3 <- function(x) sprintf("%.3f", x)
fmt6 <- function(x) sprintf("%.6f", x)

freq_coef <- freq_model_tidy$Estimate[freq_model_tidy$term == "log_freq"]
strokes_coef <- freq_model_tidy$Estimate[freq_model_tidy$term == "strokes"]
freq_pct <- (exp(freq_coef) - 1) * 100
strokes_pct <- (exp(strokes_coef) - 1) * 100
```

## Overview

This report reads pre-computed outputs from the simple demo pipeline.

- Processed data: `outputs/data/processed.csv`
- Cleaning summary: `outputs/results/cleaning.yml`
- Model metrics: `outputs/results/metrics.yml`

## Cleaning Summary

The pipeline kept `r cleaning$counts$kept_trials` of `r cleaning$counts$total_trials` trials (dropped `r cleaning$counts$dropped_trials`).
Settings: correct-only = `r cleaning$trimming$correct_only`, RT range = `r cleaning$trimming$rt_min_ms`–`r cleaning$trimming$rt_max_ms` ms.

```{r}
data.frame(
  setting = c("correct_only","rt_min_ms","rt_max_ms","total_trials","kept_trials","dropped_trials"),
  value = c(
    as.character(cleaning$trimming$correct_only),
    cleaning$trimming$rt_min_ms,
    cleaning$trimming$rt_max_ms,
    cleaning$counts$total_trials,
    cleaning$counts$kept_trials,
    cleaning$counts$dropped_trials
  )
)

```
## RT Histogram (kept trials)

```{r}
knitr::include_graphics(fig_path)
```

## Model Metrics

Model: `r metrics$model`  (N = `r N`)

R² = `r fmt3(as.numeric(metrics$r2))`.

```{r}
#| label: optional-metrics
cat(paste0("Adjusted R² = ", fmt3(as.numeric(metrics$adj_r2)), ".\n\n"))
cat(paste0("Residual sigma = ", fmt3(as.numeric(metrics$sigma)), ".\n\n"))
cat("Information criteria:\n\n")
print(data.frame(
  metric = c("AIC", "BIC"),
  value = c(fmt3(as.numeric(metrics$aic)), fmt3(as.numeric(metrics$bic)))
))
```

Coefficients:

```{r}
data.frame(
  term = c("intercept","log_freq","strokes"),
  estimate = c(
    fmt6(as.numeric(metrics$coefficients$intercept)),
    fmt6(as.numeric(metrics$coefficients$log_freq)),
    fmt6(as.numeric(metrics$coefficients$strokes))
  )
)
```

## Character Frequency Model

Character-level summaries (`outputs/data/character_frequency_model_data.csv`) were modelled with median lexical decision times as the outcome and predictors `log_freq` and `strokes`.

```{r}
knitr::kable(freq_model_tidy, digits = 3)
```

95% uncertainty for the combined fit: R² = `r fmt3(freq_model_glance$r_squared)`, sigma = `r fmt3(freq_model_glance$sigma)`.

- `log_freq`: `r fmt3(freq_coef)` on the log scale → `r fmt3(freq_pct)`% faster median responses per one-unit increase in log frequency.
- `strokes`: `r fmt3(strokes_coef)` on the log scale → `r fmt3(strokes_pct)`% slower median responses per additional stroke.

```{r}
knitr::include_graphics(freq_fig_path)
```

Median response times fall sharply from rare to moderately frequent characters, but the loess curve flattens once log frequency exceeds roughly 3, suggesting diminishing speed gains for the most common characters. The widening confidence band at high frequency reflects the sparse sample, so the apparent plateau should be revisited when more characters are available, yet the current evidence aligns with classic frequency saturation once visual complexity is held constant.
