---
title: "Agentic AI Demo Report"
format:
  html:
    toc: true
  pdf:
    toc: true
    pdf-engine: tectonic
  docx: default
  gfm: default
freeze: true
execute:
  echo: true
---

```{r}
#| label: setup
#| message: false
library(yaml)
library(readr)
library(dplyr)

metrics_path <- here::here("outputs","results","metrics.yml")
cleaning_path <- here::here("outputs","results","cleaning.yml")
fig_path <- here::here("outputs","figures","rt_hist.png")
freq_summary_path <- here::here("outputs","data","character_frequency_rt_summary.csv")
freq_curve_path <- here::here("outputs","data","frequency_rt_curve.csv")
freq_summary_text_path <- here::here("outputs","results","frequency_rt_summary.md")
freq_fig_path <- here::here("outputs","figures","frequency_vs_rt.png")

metrics <- yaml::read_yaml(metrics_path)
cleaning <- yaml::read_yaml(cleaning_path)
N <- as.integer(metrics$n_obs)

# helpers for formatting
fmt3 <- function(x) sprintf("%.3f", x)
fmt6 <- function(x) sprintf("%.6f", x)
```

## Overview

This report reads pre-computed outputs from the simple demo pipeline.

- Processed data: `outputs/data/processed.csv`
- Cleaning summary: `outputs/results/cleaning.yml`
- Model metrics: `outputs/results/metrics.yml`

## Cleaning Summary

The pipeline kept `r cleaning$counts$kept_trials` of `r cleaning$counts$total_trials` trials (dropped `r cleaning$counts$dropped_trials`).
Settings: correct-only = `r cleaning$trimming$correct_only`, RT range = `r cleaning$trimming$rt_min_ms`–`r cleaning$trimming$rt_max_ms` ms.

```{r}
data.frame(
  setting = c("correct_only","rt_min_ms","rt_max_ms","total_trials","kept_trials","dropped_trials"),
  value = c(
    as.character(cleaning$trimming$correct_only),
    cleaning$trimming$rt_min_ms,
    cleaning$trimming$rt_max_ms,
    cleaning$counts$total_trials,
    cleaning$counts$kept_trials,
    cleaning$counts$dropped_trials
  )
)

```
## RT Histogram (kept trials)

```{r}
knitr::include_graphics(fig_path)
```

## Model Metrics

Model: `r metrics$model`  (N = `r N`)

R² = `r fmt3(as.numeric(metrics$r2))`.

```{r}
#| label: optional-metrics
cat(paste0("Adjusted R² = ", fmt3(as.numeric(metrics$adj_r2)), ".\n\n"))
cat(paste0("Residual sigma = ", fmt3(as.numeric(metrics$sigma)), ".\n\n"))
cat("Information criteria:\n\n")
print(data.frame(
  metric = c("AIC", "BIC"),
  value = c(fmt3(as.numeric(metrics$aic)), fmt3(as.numeric(metrics$bic)))
))
```

Coefficients:

```{r}
data.frame(
  term = c("intercept","log_freq","strokes"),
  estimate = c(
    fmt6(as.numeric(metrics$coefficients$intercept)),
    fmt6(as.numeric(metrics$coefficients$log_freq)),
    fmt6(as.numeric(metrics$coefficients$strokes))
  )
)
```

## Frequency Effect on Recognition Speed

```{r}
#| label: frequency-load
#| message: false
character_frequency <- readr::read_csv(freq_summary_path, show_col_types = FALSE)
frequency_curve <- readr::read_csv(freq_curve_path, show_col_types = FALSE)
```

```{r}
#| label: frequency-figure
knitr::include_graphics(freq_fig_path)
```

```{r}
#| label: frequency-deciles
character_frequency |>
  mutate(decile = ntile(frequency, 10)) |>
  group_by(decile) |>
  summarise(
    freq_range = sprintf(
      "%s–%s",
      scales::comma(round(min(frequency), 1)),
      scales::comma(round(max(frequency), 1))
    ),
    mean_rt_ms = round(mean(mean_rt_ms), 1),
    .groups = "drop"
  )
```

```{r}
#| label: frequency-summary
#| results: asis
cat(readr::read_file(freq_summary_text_path))
```
