---
title: "Agentic AI Demo Report"
format:
  html:
    toc: true
  pdf:
    toc: true
    pdf-engine: tectonic
  docx: default
  gfm: default
freeze: true
execute:
  echo: true
---

```{r}
#| label: setup
#| message: false
library(yaml)

metrics_path <- here::here("outputs","results","metrics.yml")
cleaning_path <- here::here("outputs","results","cleaning.yml")
fig_path <- here::here("outputs","figures","rt_hist.png")

stopifnot(file.exists(metrics_path))
stopifnot(file.exists(cleaning_path))
stopifnot(file.exists(fig_path))

metrics <- yaml::read_yaml(metrics_path)
cleaning <- yaml::read_yaml(cleaning_path)

stopifnot(!is.null(metrics$n_obs))
N <- as.integer(metrics$n_obs)
stopifnot(!is.na(N))

# helpers for formatting
fmt3 <- function(x) sprintf("%.3f", x)
fmt6 <- function(x) sprintf("%.6f", x)
```

## Overview

This report reads pre-computed outputs from the simple demo pipeline.

- Processed data: `outputs/data/processed.csv`
- Cleaning summary: `outputs/results/cleaning.yml`
- Model metrics: `outputs/results/metrics.yml`

## Cleaning Summary

The pipeline kept `r cleaning$counts$kept_trials` of `r cleaning$counts$total_trials` trials (dropped `r cleaning$counts$dropped_trials`).
Settings: correct-only = `r cleaning$trimming$correct_only`, RT range = `r cleaning$trimming$rt_min_ms`–`r cleaning$trimming$rt_max_ms` ms.

```{r}
data.frame(
  setting = c("correct_only","rt_min_ms","rt_max_ms","total_trials","kept_trials","dropped_trials"),
  value = c(
    as.character(cleaning$trimming$correct_only),
    cleaning$trimming$rt_min_ms,
    cleaning$trimming$rt_max_ms,
    cleaning$counts$total_trials,
    cleaning$counts$kept_trials,
    cleaning$counts$dropped_trials
  )
)
```

## Model Metrics

Model: `r metrics$model`  (N = `r N`)

R² = `r fmt3(as.numeric(metrics$r2))`.

Coefficients:

```{r}
data.frame(
  term = c("intercept","log_freq","strokes"),
  estimate = c(
    fmt6(as.numeric(metrics$coefficients$intercept)),
    fmt6(as.numeric(metrics$coefficients$log_freq)),
    fmt6(as.numeric(metrics$coefficients$strokes))
  )
)
```

## RT Histogram (kept trials)

```{r}
knitr::include_graphics(fig_path)
```
